\documentclass[line]{res}

\setlength{\topmargin}{-0.9in}  % Start text higher on the page 
\setlength{\textheight}{10.2in}  % increase textheight to fit more on a page
\setlength{\headsep}{0.2in}     % space between header and text
\setlength{\headheight}{12pt}   % make room for header

\begin{document}

\moveleft.5\hoffset\centerline{\Huge\textbf{Stephen Weeks}}

\address{408.702.4448 tene@allalone.org}

\begin{resume}

\section{Work Experience}
\textbf{Apple} Site Reliability Engineer, Security Engineer - Jan 2018 - February 2024
\begin{itemize}
\item Led cross-team initiative to enable TPM-attested host certificates across 70,000 Kubernetes servers with near-real-time updates from multiple sources of truth.
\item Led system monitoring and alerting infrastructure bringup for new China iCloud environment, overcoming political, integration, and data sovereignty requirements.
\item On-call for Apple's largest systems monitoring and alerting platform.
\item Migrated stateful legacy monitoring and alerting system to Kubernetes.
\item Developed automation for injecting identity services agent in AWS and GCP k8s clusters.
\item Automated kernel upgrades for hundreds of Percona XtraDB clusters.
\item Maintained identity services agent written in Rust.
\item Supported LDAP, IAM, and other identity services.
\item Trained team on Kubernetes use, maintenance, and deployment.
\item Taught Beginner and Intermediate Rust classes.
\end{itemize}

\textbf{Instart Logic} Senior Systems Engineer - May 2017 - Jan 2018
\begin{itemize}
\item Configuration management and provisioning automation.
\end{itemize}

\textbf{IMVU} Lead Site Reliability Engineer, Engineering Manager - February 2014 - May 2017
\begin{itemize}
\item Led a site reliability team with 7 direct reports since January 2016.
\item Led project to adopt ElasticSearch for logging.
\item Led project to take MySQL backups from days down to hours.
\item Led project to migrate memcached into kubernetes.
\item Deployed Ceph for Network Storage.
\end{itemize}

\textbf{Google} Site Reliability Engineer, February 2013 - February 2014
\begin{itemize}
\item Maintenance and on-call shifts for Social Frontend.
\item Improved monitoring of stale deployments.
\end{itemize}

\textbf{IMVU} Sysadmin, April 2010 - February 2013
\begin{itemize}
\item Maintained a cluster of approximately 700 servers providing service to approximately 100k concurrent users.
\item Regular on-call shifts with a 15 minute SLA.
\item Wrote new tools in Perl to manage infrastructure and automation.
\item Reduced complexity and increased test coverage of configuration management.
\item Trained engineers for production access in devops roles.
\end{itemize}

\textbf{Guru Labs} Instructor, July 2007 - April 2010
\begin{itemize}
\item Taught week-long linux sysadmin classes, for Red Hat, IBM, HP, Oracle, and others including fundamentals, network services, troubleshooting, shell scripting, perl, and security.
\item Developed courseware for new topics.
\item Implemented and maintained Asterisk PBX.
\item Produced automation tools to aid courseware and exam development.
\end{itemize}

\textbf{Iodynamics} Junior Engineer, March 2005 - July 2007
\begin{itemize}
\item Maintained network infrastructure and web, email, and file servers for local small businesses.
\item Developed and customized web applications using Apache, mod\_perl, PostgreSQL, and PHP.
\end{itemize}

\section{Skills}

\textbf{Programming and Markup Languages}
\begin{itemize}
\item Proficient with Rust, Python, Perl, C, bash, regular expressions, SQL.
\item Some experience with Haskell, Go, Ruby, PHP, JavaScript, HTML, CSS.
\end{itemize}

\textbf{Tools and Systems}
\begin{itemize}
\item Proficient with Kubernetes, Docker, Apache HTTP Server, Nginx, Haproxy, Ceph, MySQL, Redis, Memcached, iptables, OpenSSH, git, linux kernel and userland.
\item Some experience with Prometheus, Grafana, AWS, Puppet, Pulumi, Varnish, Apache Traffic Server, SQUID, PXE, Nagios, Elastic Search, Keepalived, SELinux, Auditd, BIND, OpenSSL, Postfix, Sendmail, PostgreSQL, NFS, Samba, Subversion, OpenLDAP, Kerberos, CFEngine.
\end{itemize}

\end{resume}
\end{document}
