\documentclass[line]{res}

\setlength{\topmargin}{-0.6in}  % Start text higher on the page 
\setlength{\textheight}{9.8in}  % increase textheight to fit more on a page
\setlength{\headsep}{0.2in}     % space between header and text
\setlength{\headheight}{12pt}   % make room for header

\begin{document}

\moveleft.5\hoffset\centerline{\Huge\textbf{Stephen Weeks}}

\address{801.634.5859 tene@allalone.org}

\begin{resume}

\section{Work Experience}
\textbf{IMVU} Sysadmin, April 2010 - Present
\begin{itemize}
\item On a team of five maintaining a cluster of approximately 700 servers providing service to approximately 100k concurrent users.
\item Regular on-call shifts with a 15 minute SLA.
\item Wrote new tools in Perl to manage infrastructure and automation.
\item Reduced complexity and increased test coverage of configuration management.
\item Trained engineers for production access in devops roles.
\end{itemize}

\textbf{Guru Labs} Instructor, July 2007 - April 2010
\begin{itemize}
\item Taught week-long linux sysadmin classes, both entry level and advanced, for Red Hat, IBM, HP, Oracle, others.
\item Classes I've taught include: Linux Fundamentals, Enterprise Linux System Administration, Enterprise Linux Networking Services, Linux Troubleshooting, Shell Scripting, Learning Perl, Linux for Unix Administrators, Red Hat Networking and Security Administration.
\item Consistently high ratings on student feedback in all levels of classes.
\item Developed courseware for new topics.
\item Implemented and maintained Asterisk PBX.
\item Produced automation tools to aid courseware development.
\item Produced tools to extract questions from courseware and administer in-class exams.
\end{itemize}

\textbf{Iodynamics} Junior Engineer, March 2005 - July 2007
\begin{itemize}
\item Iodynamics was an IT consulting firm; I worked on a wide, rapidly-changing variety of projects, including the following:
\item Maintained network infrastructure and web, email, and file servers for local small businesses.
\item Developed and customized web applications using Apache, mod\_perl, PostgreSQL, and PHP.
\item Responded to security compromises, including rebuilding the compromised system and providing or implementing recommendations for improved security.
\end{itemize}

\section{Skills}

\textbf{Programming and Markup Languages}
\begin{itemize}
\item Proficient with Perl, C, bash, regular expressions, SQL.
\item Some experience with Haskell, Python, Ruby, PHP, JavaScript, HTML, CSS.
\end{itemize}

\textbf{Tools and Systems}
\begin{itemize}
\item Proficient with Apache, Nginx, MySQL, Redis, Memcached, Nagios, iptables, OpenSSH, BIND, git, PXE, linux kernel and userland.
\item Some experience with SELinux, Auditd, Postfix, Sendmail, PostgreSQL, NFS, Samba, Subversion, OpenLDAP, Kerberos, SQUID.
\end{itemize}

\end{resume}
\end{document}
