\documentclass[line]{res}

\setlength{\topmargin}{-0.9in}  % Start text higher on the page 
\setlength{\textheight}{10.2in}  % increase textheight to fit more on a page
\setlength{\headsep}{0.2in}     % space between header and text
\setlength{\headheight}{12pt}   % make room for header

\begin{document}

\moveleft.5\hoffset\centerline{\Huge\textbf{Stephen Weeks}}

\address{408.702.4448 tene@allalone.org}

\begin{resume}

\section{Work Experience}
\textbf{Apple} Security Engineer, Site Reliability Engineer - Jan 2018 - April 2024
\begin{itemize}
\item Lead system monitoring and alerting infrastructure bringup for new China iCloud environment.
\item Migrated stateful legacy monitoring system to Kubernetes.
\item Trained team on Kubernetes use, maintenance, and deployment.
\item Automated kernel upgrades for hundreds of Percona XtraDB clusters.
\item Supported LDAP, IAM, and other identity services.
\item Developed automation for ingesting and deploying TPM host certificates for cluster identity.
\item Developed and maintained identity services agent.
\item Developed automation for injecting identity services in AWS and GCP k8s clusters via Pulumi.
\end{itemize}

\textbf{Instart Logic} Senior Systems Engineer - May 2017 - Jan 2018
\begin{itemize}
\item Configuration management and provisioning automation
\end{itemize}

\textbf{IMVU} Lead Site Reliability Engineer, Engineering Manager - February 2014 - May 2017
\begin{itemize}
\item Leading a site reliability team with 7 direct reports since January 2016.
\item Lead project to adopt ElasticSearch for logging.
\item Lead project to take MySQL backups from days down to hours.
\item Lead project to migrate memcached into kubernetes.
\item Deployed Ceph for Network Storage.
\end{itemize}

\textbf{Google} Site Reliability Engineer, February 2013 - February 2014
\begin{itemize}
\item Regular on-call shifts.
\item Improved monitoring of stale deployments.
\end{itemize}

\textbf{IMVU} Sysadmin, April 2010 - February 2013
\begin{itemize}
\item On a team of five maintaining a cluster of approximately 700 servers providing service to approximately 100k concurrent users.
\item Regular on-call shifts with a 15 minute SLA.
\item Wrote new tools in Perl to manage infrastructure and automation.
\item Reduced complexity and increased test coverage of configuration management.
\item Trained engineers for production access in devops roles.
\end{itemize}

\textbf{Guru Labs} Instructor, July 2007 - April 2010
\begin{itemize}
\item Taught week-long linux sysadmin classes, for Red Hat, IBM, HP, Oracle, and others including fundamentals, network services, troubleshooting, shell scripting, perl, and security.
\item Developed courseware for new topics.
\item Implemented and maintained Asterisk PBX.
\item Produced automation tools to aid courseware and exam development.
\end{itemize}

\textbf{Iodynamics} Junior Engineer, March 2005 - July 2007
\begin{itemize}
\item Iodynamics was an IT consulting firm; I worked on a wide, rapidly-changing variety of projects, including the following:
\item Maintained network infrastructure and web, email, and file servers for local small businesses.
\item Developed and customized web applications using Apache, mod\_perl, PostgreSQL, and PHP.
\item Responded to security compromises, including rebuilding the compromised system and providing or implementing recommendations for improved security.
\end{itemize}

\section{Skills}

\textbf{Programming and Markup Languages}
\begin{itemize}
\item Proficient with Rust, Python, Perl, C, bash, regular expressions, SQL.
\item Some experience with Haskell, Go, Ruby, PHP, JavaScript, HTML, CSS.
\end{itemize}

\textbf{Tools and Systems}
\begin{itemize}
\item Proficient with Kubernetes, Docker, Apache HTTP Server, Nginx, Haproxy, Ceph, MySQL, Redis, Memcached, iptables, OpenSSH, git, linux kernel and userland.
\item Some experience with Prometheus, Grafana, AWS, Pulumi, Varnish, Apache Traffic Server, SQUID, PXE, Nagios, Elastic Search, Keepalived, SELinux, Auditd, BIND, OpenSSL, Postfix, Sendmail, PostgreSQL, NFS, Samba, Subversion, OpenLDAP, Kerberos, CFEngine.
\end{itemize}

\end{resume}
\end{document}
