\documentclass[line]{res}

\setlength{\topmargin}{-0.9in}  % Start text higher on the page 
\setlength{\textheight}{10.2in}  % increase textheight to fit more on a page
\setlength{\headsep}{0.2in}     % space between header and text
\setlength{\headheight}{12pt}   % make room for header

\begin{document}

\moveleft.5\hoffset\centerline{\Huge\textbf{Stephen Weeks}}

\address{801.634.5859 tene@allalone.org}

\begin{resume}

\section{Work Experience}
\textbf{IMVU} Lead Site Reliability Engineer, Engineering Manager February 2014 - Present
\begin{itemize}
\item Leading a site reliability team with 7 direct reports.
\item Lead project to adopt ElasticSearch for logging.
\item Lead project to take MySQL backups from days down to hours.
\item Lead project to migrate memcached into kubernetes.
\item Deployed Ceph for Network Storage.
\item Diagnosed and fixed networking problems responsible for 5x increase in peak application response time.
\end{itemize}

\textbf{Google} Site Reliability Engineer, February 2013 - February 2014
\begin{itemize}
\item Regular on-call shifts.
\item Improved monitoring of stale deployments.
\end{itemize}

\textbf{IMVU} Sysadmin, April 2010 - February 2013
\begin{itemize}
\item On a team of five maintaining a cluster of approximately 700 servers providing service to approximately 100k concurrent users.
\item Regular on-call shifts with a 15 minute SLA.
\item Wrote new tools in Perl to manage infrastructure and automation.
\item Reduced complexity and increased test coverage of configuration management.
\item Trained engineers for production access in devops roles.
\end{itemize}

\textbf{Guru Labs} Instructor, July 2007 - April 2010
\begin{itemize}
\item Taught week-long linux sysadmin classes, for Red Hat, IBM, HP, Oracle, and others including fundamentals, network services, troubleshooting, shell scripting, perl, and security.
\item Developed courseware for new topics.
\item Implemented and maintained Asterisk PBX.
\item Produced automation tools to aid courseware and exam development.
\end{itemize}

\textbf{Iodynamics} Junior Engineer, March 2005 - July 2007
\begin{itemize}
\item Iodynamics was an IT consulting firm; I worked on a wide, rapidly-changing variety of projects, including the following:
\item Maintained network infrastructure and web, email, and file servers for local small businesses.
\item Developed and customized web applications using Apache, mod\_perl, PostgreSQL, and PHP.
\item Responded to security compromises, including rebuilding the compromised system and providing or implementing recommendations for improved security.
\end{itemize}

\section{Skills}

\textbf{Programming and Markup Languages}
\begin{itemize}
\item Proficient with Haskell, Perl, C, bash, regular expressions, SQL.
\item Some experience with Rust, Go, Python, Ruby, PHP, JavaScript, HTML, CSS.
\end{itemize}

\textbf{Tools and Systems}
\begin{itemize}
\item Proficient with Apache HTTP Server, Nginx, Haproxy, Varnish, Apache Traffic Server, Ceph, MySQL, Redis, Memcached, Nagios, iptables, OpenSSH, BIND, git, PXE, linux kernel and userland.
\item Some experience with Elastic Search, Kubernetes, Docker, Keepalived, SELinux, Auditd, OpenSSL, Postfix, Sendmail, PostgreSQL, NFS, Samba, Subversion, OpenLDAP, Kerberos, SQUID.
\end{itemize}

\end{resume}
\end{document}
